Revisiting the hydrodynamic modulation of short waves by longer waves

### 2024-09-24 paper/paper.tex
Edit in intro
Incorporate diagram

\begin{abstract}
Hydrodynamic modulation of short ocean surface waves by longer ambient waves is
a well-known ocean surface process that affects remote sensing, the
interpretation of \textit{in situ} wave measurements, and numerical wave
forecasting.
In this paper, we revisit the linear wave theory and derive higher-order
solutions for the change of short-wave wavenumber, action density, and
gravitational acceleration due to the presence of longer waves.
We validate the analytical solutions with numerical simulations of the full wave
crest and action conservation equations.
The nonlinear analytical solutions of short-wave wavenumber, amplitude, and
steepness modulation significantly deviate from the linear analytical solutions
of \citet{longuet1960changes}, and are similar to the nonlinear numerical
solutions by \citet{longuet1987propagation} and \citet{zhang1990evolution}.
We also examine the result of \citet{peureux2021unsteady} who found through
numerical simulations that the short-wave modulation grows unsteadily with
each long-wave phase.
We show that this unsteady growth only occurs for homogeneous initial
conditions and does not occur for more realistic long-wave groups.
The combined analytical and numerical framework presented here allows
quantifying the importance of various terms in the full wave conservation
equations.
The proposed analytical solutions are a good approximation of the fully
nonlinear numerical solutions in long-wave steepness up to $\approx 0.2$.
\end{abstract}

@@

Short ocean surface waves are hydrodynamically modulated by longer swell.
Following \citet{unna1941white,unna1942waves,unna1947sea},
\citet{longuet1960changes} introduced a steady, approximate solution for
hydrodynamic modulation of short waves by longer waves:

\begin{equation}
\label{eq:lhs1960wavenumber}
\widetilde{k} = k (1 + \varepsilon_L)
\end{equation}
where $\widetilde{k}$ and $k$ are the modulated and unmodulated short-wave wavenumbers,
respectively, and $\varepsilon_L = a_L k_L$ is the steepness of the long wave with
wavenumber $k_L$ and amplitude $a_L$.
This hydrodynamic modulation process was instrumental for the development and
interpretation of remote sensing of ocean surface waves and currents
\citep{keller1975microwave,hara1994hydrodynamic}, and is distinguished
from the aerodynamic modulation process \citep{donelan1987effect,belcher1999wave,chen2000effects}.
\citet{phillips1981dispersion} and \citet{longuet1987propagation} revisited the
hydrodynamic modulation problem by considering nonlinear long waves and
variations in the effective gravity of short waves.
Their results yielded significantly stronger modulation than previously predicted.
\citet{henyey1988energy} derived an analytical solution for the modulation of
short waves by long waves using Hamiltonian mechanics and reported the modulation
of similar magnitude to that of \citet{longuet1987propagation}.
\citet{zhang1990evolution} considered weakly nonlinear short waves
using a non-linear Schr\" odinger equation and found stronger wavenumber
modulation but weaker amplitude modulation than those predicted by
\citet{longuet1987propagation}.
The variety of analytical and numerical frameworks (Eulerian, Hamiltonian,
Schr\" odinger) that relatively closely reproduce steady solutions for short-wave
modulation suggests that the solutions are robust.
Alternative analytical and numerical approaches to the modulation problem remain
of interest, especially if higher degrees of nonlinearity can be considered
using simpler approaches.

@@

>>>>

\begin{abstract}
Hydrodynamic modulation of short ocean surface waves by longer ambient waves is
a well-known ocean surface process that affects remote sensing, the
interpretation of \textit{in situ} wave measurements, and numerical wave
forecasting.
In this paper, we revisit the linear wave theory and derive higher-order
steady solutions for the change of short-wave wavenumber, action density, and
gravitational acceleration due to the presence of longer waves.
We validate the analytical solutions with numerical simulations of the full wave
crest and action conservation equations.
The nonlinear analytical solutions of short-wave wavenumber, amplitude, and
steepness modulation significantly deviate from the linear analytical solutions
of \citet{longuet1960changes}, and are similar to the nonlinear numerical
solutions by \citet{longuet1987propagation} and \citet{zhang1990evolution}.
We further examine the result of \citet{peureux2021unsteady} who found through
numerical simulations that the short-wave modulation grows unsteadily with
each long-wave passage.
We show that this unsteady growth only occurs only for homogeneous initial
conditions as a special case and does not generally occur, for example in more
realistic long-wave groups.
The combined analytical and numerical framework presented here allows
quantifying the importance of various terms in the full wave conservation
equations.
The proposed analytical solutions are a good approximation of the fully
nonlinear numerical solutions in long-wave steepness up to $\approx 0.2$.
As a corollary, except for a subset of initial conditions, the solutions to
fully nonlinear crest-action conservation equations are mostly steady in the
reference frame of the long waves.
\end{abstract}

@@

Short ocean surface waves are hydrodynamically modulated by longer swell.
As long waves propagate through a field of shorter waves, their orbital
velocities cause near-surface convergence and divergence on the front and rear
faces of the long waves, respectively.
Following \citet{unna1941white,unna1942waves,unna1947sea},
\citet{longuet1960changes} introduced a steady, approximate solution for
hydrodynamic modulation of short waves by longer waves:

\begin{equation}
\label{eq:lhs1960wavenumber}
\widetilde{k} = k (1 + \varepsilon_L)
\end{equation}
where $\widetilde{k}$ and $k$ are the modulated and unmodulated short-wave wavenumbers,
respectively, and $\varepsilon_L = a_L k_L$ is the steepness of the long wave with
wavenumber $k_L$ and amplitude $a_L$.
Hydrodynamic modulation is a key process for the development and
interpretation of remote sensing of ocean surface waves and currents
\citep{keller1975microwave,hara1994hydrodynamic}, and is distinguished
from aerodynamic modulation \citep{donelan1987effect,belcher1999wave,chen2000effects}.
\citet{phillips1981dispersion} and \citet{longuet1987propagation} revisited the
hydrodynamic modulation problem by considering nonlinear long waves and
variations in the effective gravity of short waves.
Their results yielded significantly stronger modulation than previously predicted.
\citet{henyey1988energy} derived an analytical solution for the modulation of
short waves by long waves using Hamiltonian mechanics and reported the modulation
of similar magnitude to that of \citet{longuet1987propagation}.
\citet{zhang1990evolution} considered weakly nonlinear short waves
using a non-linear Schr\" odinger equation and found stronger wavenumber
modulation but weaker amplitude modulation than those predicted by
\citet{longuet1987propagation}.
The variety of analytical and numerical frameworks (Eulerian, Hamiltonian,
Schr\" odinger) that relatively closely reproduce steady solutions for short-wave
modulation suggests that the solutions are robust.
Alternative analytical and numerical approaches to the modulation problem remain
of interest, especially if higher degrees of nonlinearity can be considered
using simpler approaches.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_hydrodynamic_modulation_diagram.pdf}
\caption{
  Diagram of the hydrodynamic modulation process.
}
\label{fig:hydrodynamic_modulation_diagram}
\end{figure}
